\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5 in,top=0.5in,right=0.5 in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{SAI SRINIVAS LAKKAKULA} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(669) 204-9148 \\ San José, CA} 
\address{\href{mailto:saisrinu.lakkakula@gmail.com}{saisrinu.lakkakula@gmail.com} \\ \href{https://saisrinivasl.me}{www.saisrinivasl.me} \\ \href{https://www.linkedin.com/in/saisrinivasl/}{linkedin.com/in/saisrinivasl/} \\ \href{https://github.com/saisrinivaslakkakula}{github.com/saisrinivaslakkakula}}   %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}

{Graduate student in Computer Engineering with 3+ years of  software development experience seeking a position of Software Development Engineering Intern.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Education}

{\bf Master of Science in Computer Engineering} {San Jose State University} \hfill {Jan 2021 - Dec 2022}\\
{\bf Course Work: }Distributed Systems, Computer Architecture, Data Sructures \& Algorithms\\
{\bf Bachelor of Technology}, Bapatla Engineering College \hfill {Sept 2013 - April 2017}\\
{\bf CourseWork} Electronic Devices, Computer Networks, Computer Programming.  
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }
Programming Languages & C, C++, Python, PHP, JavaScript\\
Software Engineering & Object-Oriented programming, Data Structures, Algorithms, Software Design.\\
Web Development & HTML, CSS, Bootstrap, JavaScript, React.js, Node.js, Express, RESTful API.\\
Tools & WinSCP,  Git, VS Code, PyCharm, IntelliJ, CLion, J-Meter\\
Databases \& Cloud  & MySQL, MongoDB, Azure, AWS EC-2, Kafka, Docker, Git\\
Operating Systems & Windows 7/10, Unix/Linux Environments (Ubuntu, CentOS), MacOS, z/OS 1.4
\end{tabular}
\end{rSection}

\begin{rSection}{EXPERIENCE}
\vspace{-0.5em}
\textbf{Software Development Engineer (I \& II)} \hfill Oct  2017 - Dec 2020\\
Capgemini Technology Services \hfill \textit{Chennai, India}
 \begin{itemize}
    \itemsep -6pt {} 
     \item Developed APIs using PHP and MongoDB for ‘Namaste Capgemini’ Android/iOS mobile application and streamlined 90\% organization’s logistic operations impacted by COVID-19.
     \item 	Performed Legacy Code Analysis using CAP360 In-house application for multiple Banking, Insurance clients. The tool identified 85\% technical debt on average and optimized MIPS effectively. 
     \item Pioneered ANTLR and Java based automatic code analysis and review tool called CAPCAR for legacy target programing languages. Peddled up technical code review process and reduced manual effort by 78\%.
     \item Accelerated 65\% of internal talent and resource management operations by designing and developing a cloud-based web application called MY360 using HTML, CSS, JavaScript, Ajax, PHP and MongoDB.
     \item Produced PHP and Java based automation scripts and considerably narrowed down (approximately 94\%) challenges in manual data conversion and mapping from mainframe to Linux based cloud platform.
     \item As part of Learning \& Development Initiative, Acted as an interim manager for 40+ college hires and facilitated training on a spectrum of next-gen technologies for 200+ associates with 99\% success rate.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{ACADEMIC PROJECTS}
\vspace{-1.5em}
\item \textbf{Uber Eats Clone}  {Replicated 90\%  functionality of Uber Eats Web Application by  incorporating system design  Concepts. The technology stack used is MongoDB, ReactJS, ExpressJS, NodeJS, git, Kafka, and AWS  }
  \vspace{-0.1em}
\item \textbf{Airplane Crash Analysis}  {Using the fundamentals of Data Mining, Analysed the metrics of airplane crashes over the years, developed predictive model to predict fatalities with the input attributes in the data.}
  \vspace{-0.2em}
\end{rSection} 

%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
\itemsep -6pt {} 
    \item 	Winner (2nd), Hackathon 2K18 conducted by Capgemini Technology Services in June 2018.
    \item	Winner(1st), Technozion 2K15 Tech Fest organized by NIT, Warangal in October 2015.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Leadership} 
\begin{itemize}
\itemsep -6pt {} 
    \item Academic Advisor - Indian Students Organization (ISO) at San Jose State University.
      \item Departmental Chief Co-ordinator -  Alumni Association, Bapatla Engineering College.
\end{itemize}


\end{rSection}


\end{document}
